Manuscript

### 2018-11-02 manuscript.Rmd

```{r}
library(bsselectR)
library(data.table)
library(ggpubr)
library(ggsignif)
library(kableExtra)
library(reshape2)
library(tidyverse)
```

@@

```{r}
WilcoxonByDrug <- function(drug, dataset, data_name) {
  use_data <- filter(dataset, Drug == drug)
  sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data, method = "wilcox.test", p.adjust.method = "BH")
  sig <- adj_signif(sig)
  sig <- sig[order(sig$p),]
  sig$Drug <- drug
  sig$Dataset <- toupper(data_name)
  return(sig)
}

@@

@@

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
```

@@

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", sep = "\t", header = TRUE)
g2p$Drug <- tolower(g2p$Drug)
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p <- subset(g2p, grepl("^CID", g2p$DrugID))

@@

## CRISPR: G2P genes

@@

## CRISPR: G2P genes and lineage

@@

## CCLE: G2P gene and drug

@@

ccle_signif_g2p_ByDrug <- lapply(unique(ccle_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_genesfilt, data_name = "ccle")
names(ccle_signif_g2p_ByDrug) <- unique(ccle_data_g2p_genesfilt$Drug)
saveRDS(ccle_signif_g2p_ByDrug, "./data_munging/rds/ccle_signif_g2p_ByDrug.rds")
```

@@

## CTRP: G2P gene and drug

@@

ctrp_signif_g2p_ByDrug <- lapply(unique(ctrp_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_genesfilt, data_name = "CTRP")
names(ctrp_signif_g2p_ByDrug) <- unique(ctrp_data_g2p_genesfilt$Drug)
saveRDS(ctrp_signif_g2p_ByDrug, "./data_munging/rds/ctrp_signif_g2p_ByDrug.rds")
```

@@

## GDSC: G2P gene and drug

@@

gdsc_signif_g2p_ByDrug <- lapply(unique(gdsc_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_genesfilt, data_name = "gdsc")
names(gdsc_signif_g2p_ByDrug) <- unique(gdsc_data_g2p_genesfilt$Drug)
saveRDS(gdsc_signif_g2p_ByDrug, "./data_munging/rds/gdsc_signif_g2p_ByDrug.rds")
```

@@

@@

@@

```{r fig.height=7, fig.width=12}
## MAD
plot_mad_point <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = MAD, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = c(0.75, 4, 0.19), y = 110, label = Test_Results_MAD)) +
  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_mad_box <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_boxplot(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.5) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

g2p_druggene_all_mad_summ_plot <- cowplot::plot_grid(plot_mad_box,
                   plot_mad_point,
                   nrow = 2,
                   rel_heights = c(1, 4))
g2p_druggene_all_mad_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")

## P-value
plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

g2p_druggene_all_p_summ_plot <- cowplot::plot_grid(plot_p_box,
                   plot_p_point,
                   nrow = 2,
                   rel_heights = c(1, 4))
g2p_druggene_all_p_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
```

```{r}
crispr_ccl <- unique(select(crispr_data, Broad_ID, CCLE_Name))
ccle_ccl <- unique(select(ccle_data, Broad_ID, CCLE_Name, accession_id))
ctrp_ccl <- unique(select(ctrp_data, Broad_ID, CCLE_Name, accession_id))
gdsc_ccl <- unique(select(gdsc_data, Broad_ID, CCLE_Name, accession_id))

>>>>

```{r}
library(bsselectR)
library(data.table)
library(ggpubr)
library(ggsignif)
library(htmlwidgets)
library(kableExtra)
library(plotly)
library(reshape2)
library(tidyverse)
```

@@

```{r}
WilcoxonByDrug <- function(drug, dataset, data_name, grouping_var) {
  if(grouping_var == "lineage") {
    grouper <- c("Hugo_Symbol", "group_general_lineage_name")
  }
  else if(grouping_var == "gene") {
    grouper <- "Hugo_Symbol"
  }
  use_data <- filter(dataset, Drug == drug)
  sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = grouper, data = use_data, method = "wilcox.test", p.adjust.method = "BH")
  sig <- adj_signif(sig)
  sig <- sig[order(sig$p),]
  sig$Drug <- drug
  sig$Dataset <- toupper(data_name)
  return(sig)
}

@@

## Save widget to new directory
```{r}
saveWidgetFix <- function (widget , file, ...) {
  ## A wrapper to saveWidget which compensates for arguable BUG in
  ## saveWidget which requires `file` to be in current working
  ## directory.
  wd <- getwd()
  on.exit(setwd(wd))
  outDir <- dirname(file)
  file <- basename(file)
  setwd(outDir);
  saveWidget(widget, file = file,...)
}
```

@@

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
```

@@

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_withGroupedLineages.csv", sep = "\t", header = TRUE, row.names = 1)
g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
g2p$Drug <- tolower(g2p$Drug)
g2p[g2p == -1] <- NA
g2p$Ref[g2p$Ref == "None"] <- NA
g2p$Alt[g2p$Alt == "None"] <- NA
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
g2p <- subset(g2p, grepl("^CID", g2p$DrugID))

@@

### G2P genes

@@

### G2P genes and lineage

@@

## CCLE

### G2P gene and drug

@@

ccle_signif_g2p_ByDrug <- lapply(unique(ccle_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_genesfilt, data_name = "ccle", grouping_var = "gene")
names(ccle_signif_g2p_ByDrug) <- unique(ccle_data_g2p_genesfilt$Drug)
saveRDS(ccle_signif_g2p_ByDrug, "./data_munging/rds/ccle_signif_g2p_ByDrug.rds")
```

@@

### G2P gene, drug, and lineage

```{r, eval=FALSE}
ccle_signif_g2p_lineage <- lapply(unique(ccle_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_genesfilt, data_name = "ccle", grouping_var = "lineage")
names(ccle_signif_g2p_lineage) <- unique(ccle_signif_g2p_lineage$Drug)
saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
```

```{r, eval=TRUE}
ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
ccle_signif_g2p_lineage <- rbindlist(ccle_signif_g2p_lineage, use.names = TRUE)
ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]

knitr::kable(ccle_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

## CTRP

### G2P gene and drug

@@

ctrp_signif_g2p_ByDrug <- lapply(unique(ctrp_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_genesfilt, data_name = "CTRP", grouping_var = "gene")
names(ctrp_signif_g2p_ByDrug) <- unique(ctrp_data_g2p_genesfilt$Drug)
saveRDS(ctrp_signif_g2p_ByDrug, "./data_munging/rds/ctrp_signif_g2p_ByDrug.rds")
```

@@

### G2P gene, drug, and lineage

```{r, eval=FALSE}
ctrp_signif_g2p_lineage <- lapply(unique(ctrp_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_genesfilt, data_name = "ctrp", grouping_var = "lineage")
names(ctrp_signif_g2p_lineage) <- unique(ctrp_signif_g2p_lineage$Drug)
saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
```

```{r, eval=TRUE}
ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
ctrp_signif_g2p_lineage <- rbindlist(ctrp_signif_g2p_lineage, use.names = TRUE)
ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]

knitr::kable(ctrp_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

## GDSC

### G2P gene and drug

@@

gdsc_signif_g2p_ByDrug <- lapply(unique(gdsc_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_genesfilt, data_name = "gdsc", grouping_var = "gene")
names(gdsc_signif_g2p_ByDrug) <- unique(gdsc_data_g2p_genesfilt$Drug)
saveRDS(gdsc_signif_g2p_ByDrug, "./data_munging/rds/gdsc_signif_g2p_ByDrug.rds")
```

@@

### G2P gene, drug, and lineage

```{r, eval=FALSE}
gdsc_signif_g2p_lineage <- lapply(unique(gdsc_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_genesfilt, data_name = "gdsc", grouping_var = "lineage")
names(gdsc_signif_g2p_lineage) <- unique(gdsc_signif_g2p_lineage$Drug)
saveRDS(gdsc_signif_g2p_lineage, "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
```

```{r, eval=TRUE}
gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
gdsc_signif_g2p_lineage <- rbindlist(gdsc_signif_g2p_lineage, use.names = TRUE)
gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]

knitr::kable(gdsc_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

### By gene

@@

```{r fig.height=5, fig.width=12}
## MAD
plot_mad_point <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = MAD, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = c(0.75, 4, 0.19), y = 110, label = Test_Results_MAD)) +
  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_mad_box <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_violin(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.75, width = 0.25) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

g2p_druggene_all_mad_summ_plot <- cowplot::plot_grid(plot_mad_box,
                   plot_mad_point,
                   nrow = 2,
                   rel_heights = c(1, 4))
g2p_druggene_all_mad_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")

## P-value
plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

g2p_druggene_all_p_summ_plot <- cowplot::plot_grid(plot_p_box,
                   plot_p_point,
                   nrow = 2,
                   rel_heights = c(1, 4))
g2p_druggene_all_p_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

```{r}
plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.html")
```

### By lineage

```{r}
g2p_druggenelin_p_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()

ccle_druggenelin_p_summ <- ccle_signif_g2p_lineage
ccle_druggenelin_p_summ$Drug_Gene <- paste0(ccle_druggenelin_p_summ$Drug, "_", ccle_druggenelin_p_summ$Hugo_Symbol)
ccle_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ccle_druggenelin_p_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ccle_druggenelin_summ$n <- ifelse(is.na(ccle_druggenelin_summ$n), 0, ccle_druggenelin_summ$n)
ccle_druggenelin_summ$InG2P <- ifelse(ccle_druggenelin_summ$n != 0, "Yes", "No")
ccle_druggenelin_summ$Dataset <- "CCLE"

ctrp_druggenelin_p_summ <- ctrp_signif_g2p_lineage
ctrp_druggenelin_p_summ$Drug_Gene <- paste0(ctrp_druggenelin_p_summ$Drug, "_", ctrp_druggenelin_p_summ$Hugo_Symbol)
ctrp_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ctrp_druggenelin_p_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ctrp_druggenelin_summ$n <- ifelse(is.na(ctrp_druggenelin_summ$n), 0, ctrp_druggenelin_summ$n)
ctrp_druggenelin_summ$InG2P <- ifelse(ctrp_druggenelin_summ$n != 0, "Yes", "No")
ctrp_druggenelin_summ$Dataset <- "CTRP"

gdsc_druggenelin_p_summ <- gdsc_signif_g2p_lineage
gdsc_druggenelin_p_summ$Drug_Gene <- paste0(gdsc_druggenelin_p_summ$Drug, "_", gdsc_druggenelin_p_summ$Hugo_Symbol)
gdsc_druggenelin_summ <- merge(g2p_druggenelin_p_tally, gdsc_druggenelin_p_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
gdsc_druggenelin_summ$n <- ifelse(is.na(gdsc_druggenelin_summ$n), 0, gdsc_druggenelin_summ$n)
gdsc_druggenelin_summ$InG2P <- ifelse(gdsc_druggenelin_summ$n != 0, "Yes", "No")
gdsc_druggenelin_summ$Dataset <- "GDSC"

g2p_druggenelin_all_summ <- rbind(ccle_druggenelin_summ, ctrp_druggenelin_summ, gdsc_druggenelin_summ)

test <- filter(filter(g2p_druggenelin_all_summ, group_general_lineage_name == "breast cancer"), Dataset == "CCLE")
test <- test[-39,]

```

```{r}
make_G2Plineage_plotly <- function(lineage_name) {
  use_data <- filter(g2p_druggenelin_all_summ, group_general_lineage_name == "lineage_name")

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  if(sum(use_data_ccle$n) > 0) {
    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
    ccle_lin_p_ttest_res <- paste0("t = ", round(ccle_lin_p_ttest$statistic, 3), ", df = ", round(ccle_lin_p_ttest$parameter, 3), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
  }
  else if(sum(use_data_ccle$n) == 0) {ccle_lin_p_ttest_res <-  NA}

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  if(sum(use_data_ctrp$n) > 0) {
    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
    ctrp_lin_p_ttest_res <- paste0("t = ", round(ctrp_lin_p_ttest$statistic, 3), ", df = ", round(ctrp_lin_p_ttest$parameter, 3), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
  }
  else if(sum(use_data_ctrp$n) == 0) {ctrp_lin_p_ttest_res <-  NA}

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  if(sum(use_data_gdsc$n) > 0) {
    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
    gdsc_lin_p_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
  }
  else if(sum(use_data_gdsc$n) == 0) {gdsc_lin_p_ttest_res <-  NA}

  g2p_druggenelin_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res))

  # plot_p_point <- ggplot(data = use_data) +
  #   facet_wrap(~ Dataset, scales = "free_x") +
  #   geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
  #   geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = max(use_data$n), label = Test_Results_p)) +
  #   labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  #   theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
  # 
  # plot_p_box <- ggplot(data = use_data) +
  #   facet_wrap(~ Dataset, scales = "free_x") +
  #   geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
  #   geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
  #   coord_flip() +
  #   labs(x = "Level A G2P\nassociation") +
  #   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
  # 
  # plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
  # 
  # saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/lineage_plotly/", lineage_name, "_g2p_evidence_plotly.html"))
}
```

```{r, eval=FALSE}
lapply(as.character(unique(g2p_druggenelin_all_summ$group_general_lineage_name)), make_G2Plineage_plotly)
```

## Cell line overlap

```{r, eval=FALSE}
crispr_ccl <- unique(select(crispr_data, Broad_ID, CCLE_Name))
ccle_ccl <- unique(select(ccle_data, Broad_ID, CCLE_Name, accession_id))
ctrp_ccl <- unique(select(ctrp_data, Broad_ID, CCLE_Name, accession_id))
gdsc_ccl <- unique(select(gdsc_data, Broad_ID, CCLE_Name, accession_id))
